CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-20 paper.Rmd
Add more notes for submission.

<!-- Message to editors: -->

<!-- This paper describes a suite of packages -->
<!-- to assist Societal Exergy Analysis practitioners to analyze -->
<!-- energy movement through society. -->
<!-- The new packages enable analysis of any country in the world -->
<!-- across timespans of decades or longer. -->
<!-- In short, the packages enable, for the first time, scalable SEA. -->

>>>>

<!-- Title: -->
<!-- CL-PFU: A suite of R packages for energy conversion chain analysis -->

<!-- Software's GIT repository: -->
<!-- https://github.com/EnergyEconomyDecoupling/CL-PFU-JOSS-Paper -->

<!-- Name of git branch containing the paper, not the path: -->
<!-- <<BLANK>> -->

<!-- Software version: -->
<!-- This submission covers several packages, each with its own current version. -->

<!-- Type of submission: -->
<!-- New submission -->

<!-- Main subject of the paper: -->
<!-- Software for societal exergy analysis -->

<!-- Message to editors: -->
<!-- This paper describes a suite of open source R packages -->
<!-- to assist Societal Exergy Analysis (SEA) practitioners to analyze -->
<!-- energy movement through society. -->
<!-- The new packages enable analysis of any country in the world -->
<!-- across timespans of decades or longer. -->
<!-- In short, the packages enable, for the first time, scalable SEA. -->
